
%%% CV template by Moacir P. de Sá Pereira as part of the Simple-CV project:
%%%
%%% http://plain-plain-text.org/projects/simple-cv/

\documentclass[%
    11pt,
  oneside
  ]{memoir}

\usepackage{enumitem}
%%% Font declarations.
%%% please see Fonts-README.md in this repo for more information.
\usepackage{fontspec} % Choose fonts intelligently
  %%% Fontspec looks for the font set in data/pdf-options.yml.
  %%% If that font does not exist, it will complain and default to Latin Modern.
  %%%
  %%% Fonts are fiddly, so the pdf-smallcaps-headings and pdf-bold-as-smallcaps
  %%% settings in data/pdf-options.yml may not work as expected.
  %%%
  %%% Included below are some advanced OpenType features that work well with
  %%% EB Garamond. You can download EB Garamond here:
  %%%
  %%% http://www.georgduffner.at/ebgaramond/download.html
  %%%
  %%% For more information on the OpenType features available for declaration,
  %%% please see part IV of the Fontspec documentation, available here:
  %%%
  %%% http://mirrors.ctan.org/macros/latex/contrib/fontspec/fontspec.pdf
    \IfFontExistsTF{Times New Roman}{%
    \setmainfont{Times New Roman}[%
              BoldFont = Times New Roman ,
        BoldFeatures = {Letters=SmallCaps} ,
            %%% These features may not work with all fonts.
      % Ligatures=Historic ,
      % Ligatures=Rare ,
      % ItalicFeatures={Style=Swash},
      Mapping=tex-text
    ]
  }{}
  
%%% PDF generation.
\usepackage[ breaklinks=true, hidelinks ]{hyperref}
\hypersetup{%
            pdftitle={Βιογραφικό Σημείωμα},
            pdfauthor={, Βαρβάρα Γαρνέλη.},
            pdfborder={0 0 0},
            breaklinks=true}

%%% Layout of the page
  \setlrmarginsandblock{.5in}{*}{*}
  \setulmarginsandblock{.5in}{*}{*}
  \setheadfoot{0pt}{\baselineskip} %%% footer is a baseline tall.
  \setheaderspaces{*}{0pt}{*}

%%% Define the (default) chapter style and choose the chapter
  \makechapterstyle{line}{%
    \setlength{\beforechapskip}{0pt}
    \setlength{\afterchapskip}{0pt}
    \renewcommand*{\chaptitlefont}{\Large\scshape}
    \renewcommand*{\printchaptertitle}[1]{%
    \chaptitlefont ##1 \smallskip\hrule\vspace{\baselineskip}
    }
  }
\chapterstyle{line}

%%% Section styling. We assume two, margin and overlapping.
\setsecnumdepth{subsubsection} %%% Keep the section counters running (see below).
%%% This gets complicated, because we need the numbers to roll over so that the
%%% subsections have an appropriate beforeskip.
  %%% using regular headings mode
      \setsecheadstyle{\large\scshape}
      \setaftersecskip{\baselineskip} %%% add a blank line after the heading
    \setlength{\parindent}{3em} %%% indent paragraphs
%%% Blank out all printed counters and their teeny spaces. Vital both for
%%% sections and subsections.
\makeatletter %%% enter into macro mode
\renewcommand{\@seccntformat}[1]{}
\makeatother %%% exit macro mode.

%%% Subsection styling. 
%%% Should someone (me) include subsections in their CV, things get complex.

\setsubsecheadstyle{\normalsize} %%% Subheads shouldn’t be big.
\setaftersubsecskip{0em} %%% Subheads should have no space after them
%%% New problem: \subsection should have no top margin, so it’s in line w/ the 
%%% section header. But if that’s the case, when a subsection appears later in
%%% the section, it looks just like a regular line. We need subsection to have
%%% conditional beforeskips, based on whether it’s the first subsection or not.
\let\oldsubsection\subsection %%% to avoid recursion
\renewcommand{\subsection}[1]{%
  \ifnumequal{\value{subsection}}{0} %%% If this is the first subsection
  {\setbeforesubsecskip{0em} \oldsubsection{#1}} %%% make beforeskip 0
  {\setbeforesubsecskip{\medskipamount} \oldsubsection{#1}} %%% else add a skip
}
  \setsubsecindent{3em} %%% In overlapped, yes.


%%% List styling. 
%%% They behave differently based on margin or regular headings.
\setlist[itemize]{nosep} %%% No gaps between list items.
  \setlist[itemize,1]{leftmargin=!,labelwidth=1em,labelindent=3em} %%% Push list in.
%%% And now the markers.
\renewcommand{\labelitemi}{•}
\renewcommand{\labelitemii}{-}
\renewcommand{\labelitemiii}{*}

\checkandfixthelayout

%%% Format footer
\copypagestyle{chapter}{plain}
  \makeoddhead{chapter}{}{}{}
  \makeoddfoot{chapter}{}{}{%
    , Βαρβάρα Γαρνέλη.,  \today, \thepage}
\pagestyle{chapter}

%%% Redefine \section to tighten vertical space
\let\oldsection\section
\renewcommand{\section}[1]{%
  \oldsection{#1}
  \leavevmode
  \par
  \vspace{\dimexpr-\baselineskip-\parskip}
}


\begin{document}

      \chapter*{Βιογραφικό Σημείωμα}
  

  \hypertarget{contact-information}{%
  \section{}\label{contact-information}}
    \begin{minipage}[t]{0.3\textwidth}
      
    \end{minipage}
    \begin{minipage}[t]{0.7\textwidth}
                                            \end{minipage}
  \hypertarget{ux3c3ux3c4ux3bfux3b9ux3c7ux3b5ux3afux3b1-ux3b5ux3c0ux3b9ux3baux3bfux3b9ux3bdux3c9ux3bdux3afux3b1ux3c2}{%
\section{Στοιχεία
Επικοινωνίας}\label{ux3c3ux3c4ux3bfux3b9ux3c7ux3b5ux3afux3b1-ux3b5ux3c0ux3b9ux3baux3bfux3b9ux3bdux3c9ux3bdux3afux3b1ux3c2}}

\begin{itemize}
\tightlist
\item
  \textbf{Ονοματεπώνυμο:} Βαρβάρα Γαρνέλη
\item
  \textbf{Διεύθυνση:} Κέρκυρα
\item
  \textbf{Τηλέφωνο:} 6974025556
\item
  \textbf{E-mail:} bgarnelisch@gmail.com
\item
  \textbf{Github:} bgarnb
\end{itemize}

\hypertarget{ux3b5ux3beux3b5ux3b9ux3b4ux3afux3baux3b5ux3c5ux3c3ux3b7}{%
\section{Εξειδίκευση:}\label{ux3b5ux3beux3b5ux3b9ux3b4ux3afux3baux3b5ux3c5ux3c3ux3b7}}

\begin{itemize}
\tightlist
\item
  \textbf{Η Πληροφορική στην Εκπαίδευση} (Computing Education)
\item
  \textbf{Υπολογιστική Σκέψη} (Computational Thinking)
\item
  \textbf{Σοβαρά Παιχνίδια} (Serious Games)
\item
  \textbf{Προγραμματισμός Υπολογιστών} (Computer Programming)
\end{itemize}

\hypertarget{ux3b5ux3baux3c0ux3b1ux3afux3b4ux3b5ux3c5ux3c3ux3b7}{%
\section{Εκπαίδευση}\label{ux3b5ux3baux3c0ux3b1ux3afux3b4ux3b5ux3c5ux3c3ux3b7}}

\begin{itemize}
\tightlist
\item
  \textbf{Διδακτορικό, Ιόνιο Πανεπιστήμιο, Τμήμα Πληροφορικής}, 2017

  \begin{itemize}
  \tightlist
  \item
    Video-game making approach in science education: exploring
    computational thinking skills development and student motivation
  \end{itemize}
\item
  \textbf{Μεταπτυχιακό Δίπλωμα στην Πληροφορική και τις Ανθρωπιστικές
  Σπουδές, Ιόνιο Πανεπιστήμιο, Τμήμα Πληροφορικής}, 2013
\item
  \textbf{Πτυχίο Παιδαγωγικών Σπουδών, ΣΕΛΕΤΕ, Τμήμα Πτυχιούχων ΑΕΙ},
  1993
\item
  \textbf{Πτυχίο Πληροφορικής, Οικονομικό Πανεπιστήμιο Αθήνας, Τμήμα
  Πληροφορικής}, 1992
\end{itemize}

\hypertarget{ux3b4ux3b7ux3bcux3bfux3c3ux3b9ux3b5ux3cdux3c3ux3b5ux3b9ux3c2}{%
\section{Δημοσιεύσεις}\label{ux3b4ux3b7ux3bcux3bfux3c3ux3b9ux3b5ux3cdux3c3ux3b5ux3b9ux3c2}}

\begin{itemize}
\tightlist
\item
  \textbf{Σε Διεθνή Περιοδικά:}
\item
  Garneli, V., Giannakos, M., \& Chorianopoulos, K. (2017). ``Serious
  games as a malleable learning medium: The effects of narrative,
  gameplay, and making on students' performance and attitudes'',
  \emph{British Journal of Educational Technology}, 48(3), 842-859.
\item
  Garneli, V., \& Chorianopoulos, K. (2018). ``Programming video games
  and simulations in science education: exploring computational thinking
  through code analysis'', \emph{Interactive Learning Environments},
  26(3), 386-401.
\item
  Garneli, V., \& Chorianopoulos, K. (2019). ``The effects of video game
  making within science content on student computational thinking skills
  and performance'' \emph{Interactive Technology and Smart Education}.
\item
  Garneli, V., Patiniotis, K., \& Chorianopoulos, K. (2019).
  ``Integrating Science Tasks and Puzzles in Computer Role Playing
  Games''. \emph{Multimodal Technologies and Interaction}, 3(3), 55.
\item
  \textbf{Σε Διεθνή Συνέδρια:}
\item
  Garneli, B., Giannakos, M. N., Chorianopoulos, K., \& Jaccheri, L.
  (2013, September). ``Learning by playing and learning by making''. In
  \emph{International Conference on Serious Games Development and
  Applications} (pp.~76-85). Springer, Berlin, Heidelberg.
\item
  Garneli, V. (2014, July). ``Instructional media and teaching methods
  for engaging children with computer programming''. In 2014 \emph{IEEE
  14th International Conference on Advanced Learning Technologies}
  (pp.~768-770). IEEE.
\item
  Garneli, V., Giannakos, M. N., \& Chorianopoulos, K. (2015, March).
  ``Computing education in K-12 schools: A review of the literature''.
  In 2015 \emph{IEEE Global Engineering Education Conference (EDUCON)}
  (pp.~543-551). IEEE.
\item
  Garneli, V., Giannakos, M. N., Chorianopoulos, K., \& Jaccheri, L.
  (2015, May). ``Serious game development as a creative learning
  experience: lessons learnt''. In 2015 \emph{IEEE/ACM 4th International
  Workshop on Games and Software Engineering} (pp.~36-42). IEEE.
\item
  Vassilakis, N., Garneli, V., Patiniotis, K., Deliyannis, I., \&
  Chorianopoulos, K. (2019, September). "Adapting a Classic Platform
  Video Game to the Carbohydrate Counting Method for Insulin-Dependent
  Diabetics. In Proceedings of the 5th \emph{EAI International
  Conference on Smart Objects and Technologies for Social Good}
  (pp.~149-154). ACM.
  (https://scholar.google.gr/citations?user=P5t-LWkAAAAJ\&hl=el)
\end{itemize}

\hypertarget{ux3b5ux3c0ux3b9ux3c3ux3c4ux3b7ux3bcux3bfux3bdux3b9ux3baux3cc-ux3b5ux3c6ux3b1ux3c1ux3bcux3bfux3c3ux3bcux3adux3bdux3bf-ux3b5ux3c1ux3b5ux3c5ux3bdux3b7ux3c4ux3b9ux3baux3cc-ux3adux3c1ux3b3ux3bf-3102017---13112019}{%
\section{Επιστημονικό / Εφαρμοσμένο / Ερευνητικό Έργο (3/10/2017 -
13/11/2019)}\label{ux3b5ux3c0ux3b9ux3c3ux3c4ux3b7ux3bcux3bfux3bdux3b9ux3baux3cc-ux3b5ux3c6ux3b1ux3c1ux3bcux3bfux3c3ux3bcux3adux3bdux3bf-ux3b5ux3c1ux3b5ux3c5ux3bdux3b7ux3c4ux3b9ux3baux3cc-ux3adux3c1ux3b3ux3bf-3102017---13112019}}

\begin{itemize}
\tightlist
\item
  \textbf{Διδακτική Εμπειρία}
\item
  Διδασκαλία του μαθήματος ``Interaction Design'' με έμφαση στη σχεδίαση
  και την κατασκευή εκπαιδευτικού λογισμικού στο πρόγραμμα Μεταπτυχιακών
  Σπουδών του Τμήματος Πληροφορικής του Ιονίου Πανεπιστημίου, αρ.
  σύμβασης 80249.14973/β5.ε, 23/11/2017 - 23/12/2017.
\item
  Διδασκαλία του μαθήματος ``Κινητά και Κοινωνικά Μέσα'', αρ. σύμβασης
  80291/15364/β5.ε, 1/3/2018 - 30/6/2018.
\item
  Διδασκαλία 3 εργαστηρίων στα πλαίσια του μαθήματος ``Συνεργατικές
  Εφαρμογές'' του ΠΜΣ του Τμήματος Πληροφορικής του Ιονίου Πανεπιστημίου
  με τίτλο ``Ψηφιακές Εφαρμογές και Καινοτομία'', 2019
\item
  Επίβλεψη της πτυχιακής του προπτυχιακού φοιτητή Σωτίδη Χρήστου με θέμα
  τη σχεδίαση και ανάπτυξη ενός εκπαιδευτικού ψηφιακού παιχνιδιού στα
  μαθηματικά σε συνεργασία με τον καθηγητή Κωνσταντίνο Χωριανόπουλο.
\item
  Επίβλεψη της διπλωματικής του μεταπτυχιακού φοιτητή Βασιλάκη Νικόλαου
  με θέμα τη σχεδίαση και ανάπτυξη ενός σοβαρού ψηφιακού παιχνιδιού
  σχετικό με την εκπαίδευση ινσουλινοεξαρτώμενων διαβητικών ασθενών σε
  συνεργασία με τον καθηγητή Κωνσταντίνο Χωριανόπουλο.
\item
  Επίβλεψη των Erasmus φοιτητών του Κωνσταντίνου Χωριανόπουλου: Santiago
  Fereira και Salvador Meira στο μάθημα ``Τεχνολογία Λογισμικού'' του
  εαρινού εξαμήνου και του Salvador Meira στο μάθημα της ``Επικοινωνίας
  Ανθρώπου Υπολογιστή'' του φθινοπωρινού εξαμήνου, 2018 - 2019.
\item
  \textbf{Άλλες Δραστηριότητες}
\item
  Οργάνωση Διήμερου Θερινού Σχολείου στις ``Εκπαιδευτικές Τεχνολογίες''
  στις 29 και 30 Σεπτέμβρη 2018 στους χώρους του Τμήματος Πληροφορικής
  του Ιονίου Πανεπιστημίου, στην Κέρκυρα.
\item
  Διαδικτυακή εκπαίδευση στο Git και στο GitHub και επιτυχής ολοκλήρωση
  της διαδικασίας για τον ρόλο του GitHub Campus Advisor στο Ιόνιο
  Πανεπιστήμιου (https://education.github.com/teachers/advisors).
\item
  Παρουσίαση του άρθρου `` Adapting a Classic Platform Video Game to the
  Carbohydrate Counting Method for Insulin-Dependent Diabetics`` στο
  συνέδριο GOODTECHS 2019 στη Βαλένθια της Ισπανίας.
\item
  Παρουσίαση του άρθρου ``Designing a 2D Platform Game with Mathematics
  Curriculum `` στο συνέδριο GALA conf 2019 στην Αθήνα.
\item
  Υποβολή ερευνητικής πρότασης ΕΛΙΔΕΚ με τίτλο ``Representing History
  through Collaborative Digital Game Making: An Interdisciplinary
  Teaching Approach'' στα πλαίσια της προκήρυξης με Α.Π. 500 /
  15-12-2017 σε συνεργασία με τον διδακτορικό φοιτητή του Tμήματος
  Ιστορίας Στουραΐτη Ηλία, τον διδακτορικό φοιτητή του Tμήματος
  Πληροφορικής Πατηνιώτη Κωνσταντίνο και υπό την επίβλεψη του
  Κωνσταντίνου Χωριανόπουλου και του Κωνσταντίνου Αγγελάκου, καθηγητών
  του Ιονίου Πανεπιστημίου.
\item
  Υποβολή της ερευνητικής πρότασης 1313 με τίτλο ``Σχεδίαση διαδικτυακού
  παιχνιδιού ρόλων για πολλούς παίκτες με περιεχόμενο απότον χώρο των
  φυσικών επιστημών'' στην πρόσκληση με Α. Π. 3605/4-7-2019 του ΕΔΒΜ σε
  συνεργασία με τον διδακτορικό φοιτητή του Τμήματος Πληροφορικής Κων/νο
  Πατηνιώτη και υπό την επίβλεψη του καθηγητή Κωνσταντίνου
  Χωριανόπουλου. Στα αποτελέσματα που βγήκαν στις 24/6/2019, η
  ερευνητική πρόταση κρίθηκε προκρινόμενη με τελικό βαθμό 87,32 και
  αναμένεται να ολοκληρωθεί η διαδικασία ένταξης.
\end{itemize}

\hypertarget{ux3c0ux3c1ux3bfux3cbux3c0ux3b7ux3c1ux3b5ux3c3ux3afux3b1}{%
\section{Προϋπηρεσία}\label{ux3c0ux3c1ux3bfux3cbux3c0ux3b7ux3c1ux3b5ux3c3ux3afux3b1}}

\begin{itemize}
\tightlist
\item
  \textbf{Δευτεροβάθμια Εκπαίδευση}

  \begin{itemize}
  \tightlist
  \item
    Διδασκαλία του μαθήματος ``Πληροφορική'', 1993 μέχρι σήμερα
  \end{itemize}
\item
  \textbf{Υπάλληλος γραφείου -- προγραμματιστής σε ναυτιλιακή εταιρεία},
  12/1991 -- 11/1992
\end{itemize}

\hypertarget{ux3beux3adux3bdux3b5ux3c2-ux3b3ux3bbux3ceux3c3ux3c3ux3b5ux3c2}{%
\section{Ξένες
Γλώσσες}\label{ux3beux3adux3bdux3b5ux3c2-ux3b3ux3bbux3ceux3c3ux3c3ux3b5ux3c2}}

\begin{itemize}
\tightlist
\item
  English.
\end{itemize}

\end{document}
